---
title: "sbaig1_assgnment1"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
  library(readr)
  library(dplyr)
  library(dummies)
  library(caret)
  library(class)
  library(reshape)
  library(reshape2)
  library(ggplot2)
  library(ISLR)
  library(e1071)
```


```{r}
setwd("C:/Users/shari/OneDrive/Desktop/Business Analytics/Sem 1/Machine Learning/ML_Assignment3")

Bankdata<- read.csv("C:/Users/shari/OneDrive/Desktop/Business Analytics/Sem 1/Machine Learning/ML_Assignment3/UniversalBank.csv")
```

##Transform Data

```{r}
Bankdata$PersonalLoan <- as.factor(Bankdata$Personal.Loan)
Bankdata$Online <- as.factor(Bankdata$Online)
Bankdata$CreditCard <- as.factor(Bankdata$CreditCard)
View(Bankdata)
set.seed(15)
```

##Partition the data into training (60%) and validation (40%) sets.
```{r}
Train_Index <- createDataPartition(Bankdata$Personal.Loan, p=0.6, list=FALSE)
Train <-Bankdata[Train_Index,]
Valid <- Bankdata[-Train_Index,]
```

#{A} - Create a pivot table for the training data with Online as a column variable, CC as a row variable, and Loan as a secondary row variable. The values inside the table should convey the count.

```{r}
Melt_Train <- melt(Train,id=c("CreditCard","Personal.Loan"),variable= "Online")
cast_Train <- dcast(Melt_Train,CreditCard+Personal.Loan~Online)
cast_Train <-cast_Train[c(1,2,14)]
cast_Train
View(cast_Train)
```

#{B} - Consider the task of classifying a customer who owns a bank credit card and is actively using online banking services. Looking at the pivot table, what is the probability that this customer will accept the loan offer?


##Answer - The probability of the customer accepting the loan is 90/888 =0.10135

##{C} Create two separate pivot tables for the training data. One will have Loan (rows) as afunction of Online (columns) and the other will have Loan (rows) as a function of CC.

```{r}
#pivot table1
Melt_Train1 <- melt(Train,id=c("Personal.Loan"),variable= "Online")
cast_Train1 <- dcast(Melt_Train1,Personal.Loan~Online)
cast_Train1 <-cast_Train1[c(1,13)]
cast_Train1
#pivot table2
Melt_Train2 <- melt(Train,id=c("CreditCard"),variable= "Online")
cast_Train2 <- dcast(Melt_Train2,CreditCard ~ Online)
cast_Train2 <-cast_Train2[c(1,14)]
cast_Train2
```

##{D} Compute the following quantities [P(A | B) means “the probability ofA given B”]: i. P(CC = 1 | Loan = 1) (the proportion of credit card holders among the loan acceptors) ii. P(Online = 1 | Loan = 1) iii. P(Loan = 1) (the proportion of loan acceptors) iv. P(CC = 1 | Loan = 0) v. P(Online = 1 | Loan = 0)vi. P(Loan = 0)

```{r}
Train_Data <- Train[c(13,10,14)]
table(Train_Data[,c(3,2)])
table(Train_Data[,c(1,2)])
table(Train_Data[,c(2)])
```
## i)   P(CC=1 | PL=1)  = 90/(798+90)= 0.10135 
ii)  P(OL=1 | PL=1)  = 180/(180+119)=0.60200 
iii) P(PL=1)         = (209+90)/3000=0.09966 
iv)  P(CC=1 | PL=0)  = 798/(798+1903)=0.29544 
v)   P(OL=1 | PL=0)  = 1607/(1607+1094)=0.59496 
vi)  P(PL=0)         = (1903+798)/3000=0.90033

#{E} Use the quantities computed above to compute the naive Bayes probability P(Loan = 1 | CC = 1, Online = 1).
=(0.10135*0.60266*0.09966)/((0.10135*0.60266*0.09966)+(0.29544*0.59496*0.90033))
= (0.00608052)/(0.00608052+0.15825548)
= 0.03700053


#{F} Compare this value with the one obtained from the pivot table in (B). Which is a more accurate estimate?
ANS:- Part B = 0.10135  and Part E = 0.03700053
      by comparing both the values part B is more accurate.
      
      
#{G} Which of the entries in this table are needed for computing P(Loan = 1 | CC = 1, Online = 1)? Run naive Bayes on the data. Examine the model output on training data, and find the entry that corresponds to P(Loan = 1 | CC = 1, Online = 1). Compare this to the number you obtained in (E).
```{r}
train.df <- Bankdata[Train_Index, ]
test.df <- Bankdata[ -Train_Index,]
train <- Bankdata[Train_Index, ]
test <- Bankdata[-Train_Index,]
nb_train = train.df[,c(10,13:14)]
nb_test = test.df[,c(10,13:14)]
naivebayes = naiveBayes(Personal.Loan~.,data=nb_train)
naivebayes
```      
